Machine Learning Approach to Soccer Player's Overall Rating Prediction

### 2021-12-11 Paper/main.tex
testset

\subsection*{Evaluate Final Model on the Test Set}

>>>>

\subsection*{Evaluate Final Model on the Test Set}
We will use the best model from hyperparameter tuning to make predictions on the testing set. Our model has never seen the test set before, so this performance should be a good indicator of how the model would perform if deployed in the real world.

\begin{center}
\includegraphics[scale=0.5]{liner.png}\\
\caption{Image 3, Linear Model for Overall Rating Prediction}\\
\includegraphics[scale=0.5]{nn.png} \\
\caption{Image 4, Neutral Network Model for Overall Rating Prediction}
\end{center}
